\documentclass[a4paper,10pt]{article}


\usepackage[utf8]{inputenc}

\usepackage{xspace}
\newcommand{\topo}{{\sc TopoSAT2}\xspace}
%opening
\title{\topo --- Rationales}
\author{Thorsten Ehlers}

\begin{document}

\maketitle

\section{Architecture}
\topo runs shared memory portfolio solvers which are interconnected via MPI. On each of the single portfolios, the thread with index $0$ handles the communication via MPI. 

\section{Export, Import}
Question: How often do I check? If I do this too often, the solving process may be harmed! How often does the import backtrack? 
\subsection{Unit clauses}
On nodes, the exchange of unit clauses is performed as in ManySAT. The solver with threadId$=0$
\begin{itemize}
 \item Remembers which unit clauses have been exported so far. Each unit clause is exported at most once. 
 \item Exports unit clauses from its trail --- this implicitly handles clauses imported locally as well. 
 \item Exports unit clauses received from solvers on its node. 
 \item When receiving a unit clause via MPI, and ``forward'' is enabled, it is placed in the send buffer immediately unless it has been exported already. 

\end{itemize}



\subsection{Binary clauses}
BIG nutzen um zu gucken, ob binäre Klauseln sinnvoll sind? 
\subsection{Other clauses}
\section{Clause transfer format}
Clauses are transfered as one big chunk of integers. 
\begin{itemize}
 \item The first integer denotes the number of unit clauses $n_u$
 \item The next $n_u$ integers encode the unit clauses 
 \item Afterwards, clauses are transfered 
    \begin{itemize}
     \item The first integer denotes the size $s_c$ of the clause
     \item The second integer denotes the LBD value
     \item The next $s_c$ integers encode the literals (written by calling toInt)
    \end{itemize}

\end{itemize}

\end{document}
